Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-20 mu/article/article.tex
Cheking bms notes.
Making spin velocities.
Continuation of article.

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external
                        % documents and URLs 
\usepackage{blindtext}  % fill text
\usepackage{color}
% \usepackage{showframe}
% \usepackage[inline]{showlabels}

@@

@@

@@

\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

For an angle $\alpha = \frac{\pi}{4}$ this expression can be reduced to 
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega)
&= \frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
2\mu^{\mathrm{abxy}}(\omega)}
{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
\label{eq:vab-90deg}
\end{align}

We also define $|\mathcal{V}^{\mathrm{a}}|$ as 
\begin{equation}\label{eq:va-mag}
|\mathcal{V}^{\mathrm{a}}| = 
\sqrt {
(\mathcal{V}^{\mathrm{ax}})^{2} +
(\mathcal{V}^{\mathrm{ay}})^{2} +
(\mathcal{V}^{\mathrm{az}})^{2} 
},
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  =& \cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}}
{|\mathcal{V}^{\mathrm{a}}|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi =& \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}
{\mathcal{V}^{\mathrm{ax}}} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{alt} % (fold)
\label{sec:results-alt}
% \subsubsection{$\mathcal{V}^{\mathrm{x}}$}
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
    {\includegraphics[width=\linewidth]{altplots/alt-magvxb-incang-4545.pdf}}
    \label{fig:alt-vx}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
    {\includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}}
    \label{fig:alt-vy}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
    structure. The maximum response zone is localized for an energy range from
    0.90\,eV to 0.93\,eV. 145$^{\circ}$ and for a polarization angle of the
    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-vab-mag}
\end{figure}
For the \emph{alt} structure we analyzed the energy range of energy from
0.6\,eV to 1.0\,eV where we found the most intense response for
$\mathcal{V}^{\mathrm{ab}}$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
\ref{fig:alt-vab-mag} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra
resulting from evaluate Eq. \eqref{eq:va-mag} using different polarization
angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We
can see that the onset of the response is when the energy of the incoming light
is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
150$^{\circ}$ is the zone of the absolute maximum response having for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. Also there is
another zone of interest for energies from 0.70\,eV to 0.74\,eV where a local
maximum is obtained.
%
From Fig. \ref{fig:alt-vx} we have that $|\mathcal{V}^{\mathrm{x}}|$reaches
values near to 30\,Km/s for the first zone mentioned before and 20\,Km/s for
the second one. 
%
We also found that the absolute maximum of the response is obtained for a
polarization angle $\alpha = 145^{\circ}$. The decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ in the corresponding $\mathcal{V}^{\mathrm{xx}}$,
$\mathcal{V}^{\mathrm{xy}}$, and $\mathcal{V}^{\mathrm{xz}}$ components is
depicted in Fig. \ref{fig:alt-vx-comp} and the decomposition of
$|\mathcal{V}^{\mathrm{y}}|$ in its corresponding $\mathcal{V}^{\mathrm{yx}}$,
$\mathcal{V}^{\mathrm{yy}}$, and $\mathcal{V}^{\mathrm{yz}}$ is shown in Fig.
\ref{fig:alt-vy} for this polarization angle.
%
Making the analysis for $|\mathcal{V}^{\mathrm{x}}|$ we can see that for the
energy range from 0.70\,eV to 0.74\,eV all the $xx$, $xy$, and $xz$ components
contribute with almost the same intensity giving a total spin-velocity near to
30\,Km/s. In the other hand, for the energy range from 0.88\,eV to 0.95\,eV
there is a major contribution coming from the $\mathcal{V}^{\mathrm{xz}}$
component resulting in a spin-velocity near to 20\,Km/s.
%
Also we notice that for the range of 0.70-0.74\,eV all the contributions are
positive while for the range of 0.88-0.95\,eV the $xx$ component remains
positive but the components $xy$ and $xz$ change in direction. This is due to
\textcolor{red}{\large a change in the spin polarization}.
%
Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$, which is almost two
times more intense than $|\mathcal{V}^{\mathrm{x}}|$, we have that for the
energy range from 0.70\,eV to 0.74\,eV the $yx$ and $yy$ components have a
lesser contribution than $yz$ but for the energy range all three components
have almost the same intensity resulting in a spin-velocity near to 50\,Km/s in
both cases.
%
Now we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
negative for the energy range from 0.65\,eV to 0.95\,eV \textcolor{red}{keeping
the same spin polarization for all this range.}

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{y}}$}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
%     145$^{\circ}$.}
%     \label{fig:alt-magvybincang1}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 145$^{\circ}$.}
%     \label{fig:alt-vyb1}
% \end{figure}

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Up (graphone)} % (fold)
% \label{sec:results-up}

@@

>>>>

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external
                        % documents and URLs 
\usepackage{blindtext}  % fill text
\usepackage{color}
\usepackage{showframe}
\usepackage[inline]{showlabels}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  INTRODUCTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% THEORY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

For an angle $\alpha = \frac{\pi}{4}$ this expression can be reduced to 
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega)
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
2\mu^{\mathrm{abxy}}(\omega)}
{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
\label{eq:vab-90deg}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Fixing velocity.}\label{sec:theory-fixvel}
Considering that we have 2D structures we fixed the velocity in the $xy$ plane
along $x$ and $y$ directions and we define $|\mathcal{V}^{\mathrm{a}}|$ as
\begin{equation}\label{eq:va-mag}
|\mathcal{V}^{\mathrm{a}}| = 
\sqrt {
(\mathcal{V}^{\mathrm{ax}})^{2} +
(\mathcal{V}^{\mathrm{ay}})^{2} +
(\mathcal{V}^{\mathrm{az}})^{2} 
},
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  =& \cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}}
{|\mathcal{V}^{\mathrm{a}}|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi =& \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}
{\mathcal{V}^{\mathrm{ax}}} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing spin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Fixing spin}\label{sec:theory-fixspin}
In a similar way we can fix in the $xy$ plane the spin direction along the $x$,
$y$, and $z$ directions and then define the magnitude of the spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}|$ in a fixed angle $\gamma_{b}$
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}| 
&=
\sqrt{
(\mathcal{V}^{\mathrm{ax}})^{2} +
(\mathcal{V}^{\mathrm{ay}})^{2} 
}, \\
\gamma_{\mathrm{b}} 
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}
{\mathcal{V}^{\mathrm{ax}}} \right),
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ axis.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Fixing spin} % (fold)
\label{sec:res-fixspin}

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \label{fig:alt-vx}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
    \label{fig:alt-vy}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
    structure. The maximum response zone is localized for an energy range from
    0.90\,eV to 0.93\,eV. 145$^{\circ}$ and for a polarization angle of the
    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-vab-mag}
\end{figure}
For the \emph{alt} structure we analyzed the energy range of energy from
0.6\,eV to 1.0\,eV where we found the most intense response for
$\mathcal{V}^{\mathrm{ab}}$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
\ref{fig:alt-vab-mag} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra
resulting from evaluate Eq. \eqref{eq:va-mag} using different polarization
angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We
can see that the onset of the response is when the energy of the incoming light
is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
150$^{\circ}$ is the zone of the absolute maximum response having for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. Also there is
another zone of interest for energies from 0.70\,eV to 0.74\,eV where a local
maximum is obtained.
%
From Fig. \ref{fig:alt-vx} we have that $|\mathcal{V}^{\mathrm{x}}|$reaches
values near to 30\,Km/s for the first zone mentioned before and 20\,Km/s for
the second one. 
%
We also found that the absolute maximum of the response is obtained for a
polarization angle $\alpha = 145^{\circ}$. The decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ in the corresponding $\mathcal{V}^{\mathrm{xx}}$,
$\mathcal{V}^{\mathrm{xy}}$, and $\mathcal{V}^{\mathrm{xz}}$ components is
depicted in Fig. \ref{fig:alt-vx-comp} and the decomposition of
$|\mathcal{V}^{\mathrm{y}}|$ in its corresponding $\mathcal{V}^{\mathrm{yx}}$,
$\mathcal{V}^{\mathrm{yy}}$, and $\mathcal{V}^{\mathrm{yz}}$ is shown in Fig.
\ref{fig:alt-vy} for this polarization angle.
%
Making the analysis for $|\mathcal{V}^{\mathrm{x}}|$ we can see that for the
energy range from 0.70\,eV to 0.74\,eV all the $xx$, $xy$, and $xz$ components
contribute with almost the same intensity giving a total spin-velocity near to
30\,Km/s. In the other hand, for the energy range from 0.88\,eV to 0.95\,eV
there is a major contribution coming from the $\mathcal{V}^{\mathrm{xz}}$
component resulting in a spin-velocity near to 20\,Km/s.
%
Also we notice that for the range of 0.70-0.74\,eV all the contributions are
positive while for the range of 0.88-0.95\,eV the $xx$ component remains
positive but the components $xy$ and $xz$ change in direction. This is due to
\textcolor{red}{\large a change in the spin polarization}.
%
Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$, which is almost two
times more intense than $|\mathcal{V}^{\mathrm{x}}|$, we have that for the
energy range from 0.70\,eV to 0.74\,eV the $yx$ and $yy$ components have a
lesser contribution than $yz$ but for the energy range all three components
have almost the same intensity resulting in a spin-velocity near to 50\,Km/s in
both cases.
%
Now we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
negative for the energy range from 0.65\,eV to 0.95\,eV \textcolor{red}{keeping
the same spin polarization for all this range.}

@@

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RES UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsection{Up (graphone)} % (fold)
% \label{sec:results-up}

@@

\section{Fixing velocity} % (fold)
\label{sec:fixing_velocity}

\begin{equation}
\mathcal{V}^\mathrm{a}_{\sigma} 
= 
\sqrt{
\mathcal{V}^\mathrm{ax} + 
\mathcal{V}^\mathrm{ay} +
\mathcal{V}^\mathrm{az}
}
\end{equation}

\begin{equation}
\mathcal{V}^\mathrm{a}_{\sigma\parallel} 
= 
\sqrt{
\mathcal{V}^\mathrm{ax} + 
\mathcal{V}^\mathrm{ay} 
}
\end{equation}

\begin{align}
\theta_{a} 
&=
\sin^{-1}
\left( 
\frac{\mathcal{V}^\mathrm{a}_{\sigma\parallel}}
{\mathcal{V}^\mathrm{a}_{\sigma}}
\right)
\\
\varphi_{a} 
&=
\sin^{-1}
\left(
\frac{\mathcal{V}^\mathrm{ay}}{\mathcal{V}^\mathrm{a}_{\sigma\parallel}}
\right)
\end{align}

% section fixing_velocity (end)

\section{Fixing spin} % (fold)
\label{sec:fixing_spin}

% section fixing_spin (end)
